An open reproducible framework for the study of the iterated prisoner's dilemma

### 2015-08-15 paper.tex
Putting initial structure of paper together
- Title
- Authors (alphabetical on first name - I don't care what we go for here)
- Sections
- Bullet points added for intro

@@

\title{Title of paper}

@@

Original paper by Axelrod and Hamilton \cite{1981-Axelrod-Hamilton}.

Some recent discussion of memory one strategies \cite{press2012iterated, stewart2012extortion}.

\bibliography{references.bib}
\bibliographystyle{unsrt}

\end{document}

>>>>

% Nicer bibliography management
\usepackage[backend=biber, backref=true, firstinits=true, url=true, isbn=true]{biblatex}
\addbibresource{references.bib}
%-----------------------------

% Lazy page formating (we can adjust when submitting)
\usepackage{fullpage}
\usepackage[parfill]{parskip}
%-----------------------------

\title{An open reproducible framework for the study of the iterated prisoner's
dilemma}

\author{Karol Langner\\
        \and
        Marc Harper\\
        \and
        Owen Campbell\\
        \and
        Vincent Knight\\
}

\date{\today}

@@

@@

\section{Introduction}\label{sec:introduction}

\begin{itemize}
\item Review of the tournament itself;
      Original paper by Axelrod and Hamilton~\cite{1981-Axelrod-Hamilton}.
      Some recent discussion of memory one strategies~\cite{press2012iterated, stewart2012extortion}.

\item Discussion about open reproducible science (there are some reference
      around) (Python, git, github etc\dots)
\item Overview of the library (what it can do, what has been done with it)
\item Point at Sections~\ref{sec:reproducing-previous-tournaments}
      and~\ref{sec:new-strategies-and-implications}.
\end{itemize}

\section{Reproducing previous tournaments}\label{sec:reproducing-previous-tournaments}

\section{New strategies and implications}\label{sec:new-strategies-and-implications}

\section{Conclusion}\label{sec:conclusion}

\printbibliography
\end{document}
